---
title: "T2.D5_LabyInoc_PrelimAnalyse"
author: "Forest Schenck"
date: "August 17, 2016"
output: pdf_document
---

#Packages Library
```{r Packages Library}
library (dplyr)
library(sciplot)

library(lme4)
library(lmerTest)

library(multcomp)

library(maps)
library(mapdata)
library(mapplots)
library(mapproj)
#library(maptools) #didn't work for shape file
#gpclibPermit() # Not permited

library(rgdal)
library(sp)

```

#uploading data
```{r Data Upload}
##Mesocosm
mesocosm.leaf <- read.csv("TRIAL2_mesocosm.csv") ##old name = d1

str(mesocosm.leaf)

mesocosm.leaf$no. <- as.factor(mesocosm.leaf$no.)
mesocosm.leaf$experiment.day <- as.factor(mesocosm.leaf$experiment.day)
mesocosm.leaf$exp.leaf.no <- as.factor(mesocosm.leaf$exp.leaf.no)
mesocosm.leaf$current.leaf.no <- as.factor(mesocosm.leaf$current.leaf.no)
mesocosm.leaf$mesocosm <- as.factor(mesocosm.leaf$mesocosm)
mesocosm.leaf$vase <- as.factor(mesocosm.leaf$vase)

mesocosm.leaf$shoot.ID <- paste(mesocosm.leaf$site, mesocosm.leaf$no.)
mesocosm.leaf$shoot.ID <- as.factor(mesocosm.leaf$shoot.ID)

## Shoot and rhizome biomass
mesocosm.shoot <- mesocosm.leaf %>%
  

## Environmental Data
d1.env <- read.csv("LabyInoc_T2_ZM_ENV_23JAN2017.csv")
dfull.env <- read.csv("DC_Temp_2016_Complete.csv")

## Field Data
d1.field <- read.csv("LabyInoc_T2_ZM_field_31JAN2017.csv")
d1.dc.field <- read.csv("DC_2016_WD_FS.csv")
```

#Day0 Analyses

##Data manipulation
```{r Day0 Data Manipulation}
d1.d0 <- filter(d1, experiment.day == "0")
str(d1.d0)

d1.d0 <- filter(d1.d0, mesocosm != "28")
```

##Lesion Spread Figures and Analyes
```{r Day0 Lesion Presence}
#Figures
  ##Infection proportion ~ site * leaf.no
bargraph.CI(x.factor = exp.leaf.no, group = site, response = lesion.presence, data = d1.d0, ylim = c(0,1), ylab = "Proportion of leaves with lesions", xlab = "Leaf number", legend = T)

  ##Infection proportion ~ infection treatment * leaf.no
bargraph.CI(x.factor = exp.leaf.no, group = infection, response = lesion.presence, data = d1.d0, ylim = c(0,1), ylab = "Proportion of leaves with lesions", xlab = "Leaf number", legend = T)
  ##Infection proportion ~ infection treatment * leaf.no (only leaves 1 and 2)
bargraph.CI(x.factor = exp.leaf.no, group = infection, response = lesion.presence, data = filter(d1.d0, exp.leaf.no == "1" | exp.leaf.no == "2"), ylim = c(0,1), ylab = "Proportion of leaves with lesions", xlab = "Leaf number", legend = T)
            
  ##Infected proportion ~ site * infection treatment
bargraph.CI(x.factor = site, group = infection, response = lesion.presence, data = d1.d0, ylim = c(0,1), ylab = "Proportion of leaves with lesions", xlab = "Site", legend = T)
  ##Infection proportion ~ site * infection (only leaves 1 and 2)
bargraph.CI(x.factor = site, group = infection, response = lesion.presence, data = filter(d1.d0, exp.leaf.no == "1" | exp.leaf.no == "2"), ylim = c(0,1), ylab = "Proportion of leaves with lesions", xlab = "Infection Expected", legend = T)


#Analyses

  ###Something wrong here and no p-values??
model.lesion.presence <- glmer(cbind(lesion.presence, lesion.absence) ~ infection*site*exp.leaf.no + (1|shoot.ID) + (1|mesocosm), data = filter(d1.d0, exp.leaf.no != "5" & exp.leaf.no != "4"), family = "binomial")
anova(model.lesion.presence, test = "LR")
```


##Lesion Percent Cover Figures and Analyses
```{r Day0 Lesion Percent Cover}
#Figures

  ##Lesion Percent Cover ~ Site * Leaf.no
bargraph.CI(x.factor = exp.leaf.no, group = site, response = lesion.pc, data = filter(d1.d0, lesion.presence == "1"), ylim = c(0,10), ylab = "Lesion percent cover", xlab = "Site", legend = T)

  ##Lesion percent cover ~ infection treatment * leaf.no
bargraph.CI(x.factor = exp.leaf.no, group = infection, response = lesion.pc, data = filter(d1.d0, lesion.presence == "1"), ylim = c(0,10), ylab = "Lesion percent cover", xlab = "Infection Expected", legend = T)

  ##Lesion percent cover ~ site * infection treatment
bargraph.CI(x.factor = site, group = infection, response = lesion.pc, data = filter(d1.d0, lesion.presence == "1" & exp.leaf.no != "4" & exp.leaf.no != "5"), ylim = c(0,10), ylab = "Lesion percent cover", xlab = "Site", legend = T)

  ##Lesion percent cover ~ site * infection treatment (including leaves without lesions)
bargraph.CI(x.factor = site, group = infection, response = lesion.pc, data = filter(d1.d0, exp.leaf.no != "4" & exp.leaf.no != "5"), ylim = c(0,10), ylab = "Lesion percent cover", xlab = "Site", legend = T)

  ##Lesion percent cover ~ site
bargraph.CI(x.factor = site, response = lesion.pc, data = filter(d1.d0, lesion.presence == "1"), ylim = c(0,100), ylab = "Lesion percent cover", xlab = "Site", legend = T)

#Analyses
model.lesion.pc.d0 <- lmer(lesion.pc ~ infection*site*exp.leaf.no + (1|shoot.ID) + (1|mesocosm), data = filter(d1.d0, lesion.presence == "1"))
anova(model.lesion.pc.d0) #main effect of site, interaction of site:leaf number, but not biologically significant! Also hard to deal with contrasts when sites have diff. amt of leaves with lesions

# Including plants WITHOUT lesions (aka including 0% values) and leaves 4 and 5 because of lack of replication at this high leaf number 
model.lesion.pc.d0.all.plants <- lmer(lesion.pc ~ infection*site*exp.leaf.no + (1|shoot.ID) + (1|mesocosm), data = filter(d1.d0, exp.leaf.no != "4" & exp.leaf.no != "5"))
anova(model.lesion.pc.d0.all.plants) #no effects significant and NO ERRORS in model.
```

##Length Figures and Analyses
```{r Day0 Leaf Length}
#Figures

  ##Length ~ infection * site
bargraph.CI(x.factor = site, group = infection, response = length.cm, data = filter(d1.d0, exp.leaf.no != "5"), ylim = c(0,30), ylab = "Leaf length (cm)", xlab = "Site", legend = T)

  ##Length ~ infection * leaf number (*only DC)
bargraph.CI(x.factor = exp.leaf.no, group = infection, response = length.cm, data = filter(d1.d0, site =="DC" & exp.leaf.no != "5"), ylim = c(0,30), ylab = "Leaf length (cm)", xlab = "Leaf number", legend = T)

  #Length ~ site * exp.leaf.no (Excluding leaves 4 and 5)
bargraph.CI(x.factor = exp.leaf.no, group = site, response = length.cm, data = filter(d1.d0, exp.leaf.no != "5" & exp.leaf.no != "4"), ylim = c(0,30), ylab = "Leaf length (cm)", xlab = "Leaf number", legend = T)

#Analyses
  ##Including all leaves in analysis
model.length.cm.d0 <- lmer(length.cm ~ infection*site*exp.leaf.no + (1|shoot.ID) + (1|mesocosm), data = d1.d0)
anova(model.length.cm.d0) ##Not all sites have multiple plants with 4th or 5th leaf

  ###Checking to see if results change if exclude leaves 4 and 5 from analyses
model.length.cm.d0.L123 <- lmer(length.cm ~ site*infection*exp.leaf.no + (1|shoot.ID) + (1|mesocosm), data = filter(d1.d0, exp.leaf.no != "4" & exp.leaf.no != "5"))
anova(model.length.cm.d0.L123) ##not change in results; error message goes away :)
```


#Day5 Analyses

##Data manipulation
```{r Day5 Data Manipulation}
d1.d5 <- filter(d1, experiment.day == "5" & mesocosm != "28")
str(d1.d5)

#Leaf Growth
d0 <- subset(d1.d0, select = c(researcher:exp.leaf.no, lesion.pc, length.cm, no.leaves, lesion.presence, lesion.absence))

d1.d5 <- merge(d1.d5, d0, all.x = TRUE, by = c("vase", "exp.leaf.no"))
d1.d5 <- subset(d1.d5, select = c(vase:shoot.ID, lesion.pc.y, length.cm.y, no.leaves.y, lesion.presence.y, lesion.absence.y))
str(d1.d5)

d1.d5$delta.sheath.length[is.na(d1.d5$delta.sheath.length)] <- 0
d1.d5$std.length.cm <- d1.d5$length.cm.x - d1.d5$delta.sheath.length

d1.d5$delta.length.cm <- d1.d5$std.length.cm - d1.d5$length.cm.y

##Lesion Percent Cover and Leaf Growth Effect Sizes
d1.d5.ef <- d1.d5 %>%
  filter(infection.x == "N") %>%
  filter(exp.leaf.no != "4" & exp.leaf.no != "5") %>%
  group_by(site.x, exp.leaf.no) %>%
  summarize(control.lpc5 = mean(lesion.pc.x, na.rm = T), control.growth5 = mean(delta.length.cm, na.rm = T))

d5.ef <- merge(d1.d5, d1.d5.ef, by = c("site.x", "exp.leaf.no"), all.x = T)

d5.ef <- d5.ef %>%
  filter(infection.x == "Y") %>%
  filter(exp.leaf.no != "4" & exp.leaf.no != "5") %>%
  subset(select = c(site.x, exp.leaf.no, vase, mesocosm.x, lesion.pc.x, delta.length.cm, control.lpc5, control.growth5))

d5.ef$lpc.ef <- (d5.ef$lesion.pc.x - d5.ef$control.lpc5)/d5.ef$control.lpc5
d5.ef$growth.ef <- (d5.ef$delta.length.cm - d5.ef$control.growth5)/d5.ef$control.growth5

#data for growth effect size figures
d5.ef.fig <- d5.ef %>%
  filter(exp.leaf.no != "0") %>%
  group_by(exp.leaf.no) %>%
  summarize(growth.ef.mean = mean(growth.ef, na.rm = T), growth.ef.95ci = 1.96*se(growth.ef))

#Leaf number
d1.d5.leaves = d1.d5 %>%
  filter(no.leaves.y != "NA") %>%
  group_by(mesocosm.x, infection.x, site.x, shoot.ID) %>%
  summarize(no.leaves.x = mean(no.leaves.x), no.leaves.y = mean(no.leaves.y), no.leaves.new = mean(no.leaves.new), no.leaves.lost = mean(no.leaves.lost))

d1.d5.leaves$delta.no.leaves <- d1.d5.leaves$no.leaves.x - d1.d5.leaves$no.leaves.y

##Leaf number effect sizes
d1.d5.leaves.ef <- d1.d5.leaves %>%
  filter(infection.x == "N") %>%
  group_by(infection.x) %>%
  summarize(control.dnl = mean(delta.no.leaves, na.rm = T), control.new = mean(no.leaves.new, na.rm = T), control.lost = mean(no.leaves.lost, na.rm =T))

#d5.leaves.ef <- merge(d1.d5.leaves, d1.d5.leaves.ef, by = c("site.x"), all.x = T)

#d5.leaves.ef <- d5.leaves.ef %>%
  #filter(infection.x == "Y") %>%
  #subset(select = c(site.x, mesocosm.x, no.leaves.new:control.lost))

d5.leaves.ef <- merge(filter(d1.d5.leaves, infection.x == "N"), d1.d5.leaves.ef, by = c("infection.x"), all.x = T)
d5.leaves.ef <- subset(d5.leaves.ef, select = c("site.x", "control.dnl", "control.new", "control.lost"))

d5.leaves.ef <- merge(d1.d5.leaves, d5.leaves.ef, by = "site.x", all.x =T)
d5.leaves.ef <- d5.leaves.ef %>%
  filter(infection.x == "Y") %>%
  group_by(infection.x, shoot.ID) %>%
  summarize(delta.no.leaves = mean(delta.no.leaves), no.leaves.new = mean(no.leaves.new), no.leaves.lost = mean(no.leaves.lost), control.dnl = mean(control.dnl), control.new = mean(control.new), control.lost = mean(control.lost))

d5.leaves.ef$dnl.ef <- (d5.leaves.ef$delta.no.leaves - d5.leaves.ef$control.dnl)/d5.leaves.ef$control.dnl
d5.leaves.ef$new.ef <- (d5.leaves.ef$no.leaves.new - d5.leaves.ef$control.new)/d5.leaves.ef$control.new
d5.leaves.ef$lost.ef <- (d5.leaves.ef$no.leaves.lost - d5.leaves.ef$control.lost)/d5.leaves.ef$control.lost
###how to deal with leaves lost being 0 for controls --> don't analyze by site

d5.leaves.ef.fig <- d5.leaves.ef %>%
  group_by(infection.x) %>%
  summarize(dnl.ef.mean = mean(dnl.ef), dnl.ef.95ci = 1.96*se(dnl.ef), new.ef.mean = mean(new.ef), new.ef.95ci = 1.96*se(new.ef), lost.ef.mean = mean(lost.ef), lost.ef.95ci = 1.96*se(lost.ef))

d5.leaves.ef.fig$infection.x <- c("")
d5.leaves.ef.fig$infection.x <- as.factor(d5.leaves.ef.fig$infection.x)
str(d5.leaves.ef.fig)
```

##Lesion Spread Figures and Analyes
```{r Day5 Lesion Presence}
#Figures

 ##Infection proportion ~ infection treatment * leaf.no
bargraph.CI(x.factor = exp.leaf.no, group = infection.x, response = lesion.presence.x, data = d1.d5, ylim = c(0,2), ylab = "Proportion of leaves with lesions", xlab = "Leaf number", legend = T)

  ##Infected proportion ~ site * infection treatment
bargraph.CI(x.factor = site.x, group = infection.x, response = lesion.presence.x, data = d1.d5, ylim = c(0,2), ylab = "Proportion of leaves with lesions", xlab = "Site", legend = T)

  ##Infection proportion ~ site * leaf.no (*Only infected)
bargraph.CI(x.factor = exp.leaf.no, group = site.x, response = lesion.presence.x, data = filter(d1.d5, infection.x == "Y"), ylim = c(0,2), ylab = "Proportion of leaves with lesions", xlab = "Site", legend = T)

#Analyses (Get glm code from Torrie 1/12/17)


```

##Lesion Percent Cover Figures and Analyses
```{r Day5 Lesion Percent Cover}
#Figures

  ## Lesion percent cover effect size ~ leaf.no (grouped by site)
bargraph.CI(x.factor = exp.leaf.no, group = site.x, response = lpc.ef, data = d5.ef, ylim = c(0,100), ylab = "Effect of disease on lesion percent cover", xlab = "Leaf number", legend = T)

  ##Lesion percent cover ~ infection treatment * leaf.no
#bargraph.CI(x.factor = exp.leaf.no, group = infection.x, response = lesion.pc.x, data = filter(d1.d5, lesion.presence.x == "1"), ylim = c(0,100), ylab = "Lesion percent cover", xlab = "Leaf number", legend = T)
    ###Lesion percent cover ~ infection treatment * leaf.no (*all leaves, excluding leaves 4 & 5)
par(mfrow = c(2,2))
bargraph.CI(x.factor = exp.leaf.no, group = infection.x, response = lesion.pc.x, data = filter(d1.d5, exp.leaf.no != "4" & exp.leaf.no != "5" & site.x == "DC"), ylim = c(0,100), ylab = "Lesion percent cover", xlab = "Leaf number", legend = T) ##DC plot
bargraph.CI(x.factor = exp.leaf.no, group = infection.x, response = lesion.pc.x, data = filter(d1.d5, exp.leaf.no != "4" & exp.leaf.no != "5" & site.x == "LP"), ylim = c(0,100), ylab = "Lesion percent cover", xlab = "Leaf number", legend = T) ##LP plot
bargraph.CI(x.factor = exp.leaf.no, group = infection.x, response = lesion.pc.x, data = filter(d1.d5, exp.leaf.no != "4" & exp.leaf.no != "5" & site.x == "NB"), ylim = c(0,100), ylab = "Lesion percent cover", xlab = "Leaf number", legend = T) ##NB plot
bargraph.CI(x.factor = exp.leaf.no, group = infection.x, response = lesion.pc.x, data = filter(d1.d5, exp.leaf.no != "4" & exp.leaf.no != "5" & site.x == "WB"), ylim = c(0,100), ylab = "Lesion percent cover", xlab = "Leaf number", legend = T) ##WB plot

  ##Lesion percent cover ~ infection treatment * leaf.no (*all leaves, excluding leaves 4 and 5)
#bargraph.CI(x.factor = exp.leaf.no, group = infection.x, response = lesion.pc.x, data = filter(d1.d5, exp.leaf.no != "4" & exp.leaf.no != "5"), ylim = c(0,100), ylab = "Lesion percent cover", xlab = "Leaf number", legend = T)

  ##Lesion percent cover ~ site * infection treatment
#bargraph.CI(x.factor = site.x, group = infection.x, response = lesion.pc.x, data = filter(d1.d5, lesion.presence.x == "1"), ylim = c(0,100), ylab = "Lesion percent cover", xlab = "Site", legend = T)

  ##Lesion Percent Cover ~ Site * Leaf.no (*Only infected)
par(mfrow = c(1,1))
bargraph.CI(x.factor =  exp.leaf.no, group =site.x, response = lesion.pc.x, data = filter(d1.d5, infection.x == "Y" & exp.leaf.no != "4" & exp.leaf.no != "5"), ylim = c(0,100), ylab = "Lesion percent cover", xlab = "Leaf number", legend = T)

  ##Lesion Percent Cover ~ Site * Leaf.no (*Only control)
par(mfrow = c(1,1))
bargraph.CI(x.factor =  exp.leaf.no, group =site.x, response = lesion.pc.x, data = filter(d1.d5, infection.x == "N" & exp.leaf.no != "4" & exp.leaf.no != "5"), ylim = c(0,5), ylab = "Lesion percent cover", xlab = "Leaf number", legend = T)

  ##Lesion Percent Cover ~ Site * Leaf.no (*Only infected and all leaves)
#bargraph.CI(x.factor = exp.leaf.no, group = site.x, response = lesion.pc.x, data = filter(d1.d5, infection.x == "Y"), ylim = c(0,100), ylab = "Lesion percent cover", xlab = "Leaf number", legend = T)

#Analyses
#model.lesion.pc.d5 <- lmer(lesion.pc.x ~ infection.x*site.x*exp.leaf.no + (1|shoot.ID) + (1|mesocosm.x) + lesion.pc.y, data = filter(d1.d5, lesion.presence.x == "1"))
#anova(model.lesion.pc.d5)

#Correct FULL model (1/23/17)
model.lesion.pc.d5.all <- lmer(lesion.pc.x ~ infection.x*site.x*exp.leaf.no + (1|shoot.ID) + (1|mesocosm.x), data = filter(d1.d5, exp.leaf.no != "4" & exp.leaf.no != "5")) ##Including leaves with 0% infection, exclude leaves 4 and 5 because of lack of replication across sites, lesion.pc.y not significant so removed from model
anova(model.lesion.pc.d5.all)

model.lesion.pc.disease.d5 <- lmer(lesion.pc.x ~ site.x*exp.leaf.no + (1|shoot.ID) + (1|mesocosm.x) + lesion.pc.y, data = filter(d1.d5, infection.x == "Y" & exp.leaf.no != "4" & exp.leaf.no != "5")) #Looking at relationship between site and leaf number within infected plants
anova(model.lesion.pc.disease.d5)

model.lesion.pc.control.d5 <- lmer(lesion.pc.x ~ site.x*exp.leaf.no + (1|shoot.ID) + (1|mesocosm.x) + lesion.pc.y, data = filter(d1.d5, infection.x == "N" & exp.leaf.no != "4" & exp.leaf.no != "5")) #Looking at relationship between site and leaf number within control plants
anova(model.lesion.pc.control.d5)

  ##Just leaf 2 of infected plants that are showing signs of lesions (aka all plants)
#model.lesion.pc.d5.leaf2 <- lmer(lesion.pc.x ~ site.x + (1|mesocosm.x) + lesion.pc.y, data = filter(d1.d5, lesion.presence.x == "1" & exp.leaf.no == "2" & infection.x == "Y"))
#anova(model.lesion.pc.d5.leaf2)
```

##Leaf Growth Figures and Analyses
```{r Day5 Leaf Growth}
 ## Growth effect size ~ leaf.no (grouped by site)
fig.growth <- barplot(c(0,0), names = d5.ef.fig$exp.leaf.no[1:2] , ylim = c(-1, 1),
                  ylab = "Effect size of disease on leaf growth",
                  xlab = "Leaf number")
points(x = fig.growth, d5.ef.fig$growth.ef.mean[1:2])
arrows(y0 = d5.ef.fig$growth.ef.mean[1:2] - d5.ef.fig$growth.ef.95ci[1:2], y1 = d5.ef.fig$growth.ef.mean[1:2] + d5.ef.fig$growth.ef.95ci[1:2], x0 = fig.growth, x1 =fig.growth, angle = 90, code = 3, #95% CI
length = 0.1)

#bargraph.CI(x.factor = exp.leaf.no, group = site.x, response = growth.ef, data = filter(d5.ef, exp.leaf.no != "3"), ylim = c(-1,1), ylab = "Effect of disease on leaf growth", xlab = "Leaf number", legend = T)

  ##Growth ~ infection treatment * leaf.no (Excluding leaves 4 and 5)
bargraph.CI(x.factor = exp.leaf.no, group = infection.x, response = delta.length.cm, data = filter(d1.d5, exp.leaf.no != "4" & exp.leaf.no != "5"), ylim = c(0,7), ylab = "Leaf growth (cm)", xlab = "Leaf number", legend = T)

  ##Growth ~ site * leaf.no 
bargraph.CI(x.factor = exp.leaf.no, group = site.x, response = delta.length.cm, data = filter(d1.d5, exp.leaf.no != "4" & exp.leaf.no != "5"), ylim = c(0,7), ylab = "Leaf growth (cm)", xlab = "Leaf number", legend = T)

#Analyses
model.growth.std.d5 <- lmer(std.length.cm ~ infection.x*site.x*exp.leaf.no + (1|shoot.ID) + (1|mesocosm.x) + length.cm.y, data = filter(d1.d5, exp.leaf.no != "4" & exp.leaf.no != "5")) #adjusting for delta sheath length (*Excluding leaves 4 and 5 because not enough reps for adequate contrasts)
anova(model.growth.std.d5) #Significant interactions: site*leaf number and Infection*leaf number
```

##Change in leaf number Figures and Analyses
```{r Day5 Leaf Number}
#Figures

##Change in leaves (effect size)
#bargraph.CI(x.factor = infection.x, response = dnl.ef, data = d5.leaves.ef, ylim = c(-5,5), ylab = "Effect of disease on change in leaf number")

fig.dnl <- barplot(0, names =d5.leaves.ef.fig$infection.x , ylim = c(-5, 5),
                  ylab = "Effect size of disease on net leaf change",
                  xlab = "")
points(x = fig.dnl[1], d5.leaves.ef.fig$dnl.ef.mean[1])
arrows(y0 = d5.leaves.ef.fig$dnl.ef.mean - d5.leaves.ef.fig$dnl.ef.95ci, y1 = d5.leaves.ef.fig$dnl.ef.mean + d5.leaves.ef.fig$dnl.ef.95ci, x0 = fig.dnl, x1 =fig.dnl, angle = 90, code = 3, #95% CI
length = 0.1)

## number of leaves lost (effect size)
fig.lost <- barplot(0, names =d5.leaves.ef.fig$infection.x , ylim = c(-35, 35),
                  ylab = "Effect size of disease on the number of leaves lost",
                  xlab = "")
points(x = fig.lost[1], d5.leaves.ef.fig$lost.ef.mean[1])
arrows(y0 = d5.leaves.ef.fig$lost.ef.mean - d5.leaves.ef.fig$lost.ef.95ci, y1 = d5.leaves.ef.fig$lost.ef.mean + d5.leaves.ef.fig$lost.ef.95ci, x0 = fig.dnl, x1 =fig.dnl, angle = 90, code = 3, #95% CI
length = 0.1)

#bargraph.CI(x.factor = infection.x, response = lost.ef, data = d5.leaves.ef, ylab = "Effect of disease on leaves lost")

## number of leaves new (effect size)
#bargraph.CI(x.factor = infection.x, response = new.ef, data = d5.leaves.ef, ylab = "Effect of disease on leaves produced")

fig.new <- barplot(0, names =d5.leaves.ef.fig$infection.x , ylim = c(-2, 2),
                  ylab = "Effect size of disease on the number of new leaves",
                  xlab = "")
points(x = fig.new[1], d5.leaves.ef.fig$new.ef.mean[1])
arrows(y0 = d5.leaves.ef.fig$new.ef.mean - d5.leaves.ef.fig$new.ef.95ci, y1 = d5.leaves.ef.fig$new.ef.mean + d5.leaves.ef.fig$new.ef.95ci, x0 = fig.dnl, x1 =fig.dnl, angle = 90, code = 3, #95% CI
length = 0.1)

  ##Change in leaves ~ infection
bargraph.CI(x.factor = infection.x, response = delta.no.leaves, data = d1.d5.leaves, ylim = c(-1,1), ylab = "Change in the number of leaves per shoot", xlab = "Infection")

  ##Number of leaves lost ~ infection
  bargraph.CI(x.factor = infection.x, response = no.leaves.lost, data = d1.d5.leaves, ylim = c(0, 1), ylab = "Number of leaves lost per shoot", xlab = "Site", legend = T)
  
  
#Analyses
model.no.leaves.d5 <- lmer(no.leaves.x ~ infection.x*site.x + (1|mesocosm.x) + no.leaves.y, data = d1.d5.leaves)
anova(model.no.leaves.d5) #Significant effect of infection

model.new.leaves.d5 <- lmer(no.leaves.new ~ infection.x*site.x + (1|mesocosm.x) + no.leaves.y, data = d1.d5.leaves)
anova(model.new.leaves.d5) # No significant effects

model.leaves.lost.d5 <- lmer(no.leaves.lost ~ infection.x*site.x + (1|mesocosm.x) + no.leaves.y, data = d1.d5.leaves)
anova(model.leaves.lost.d5) #Significant main effect of infection, marginal effect of site (P = 0.056)
```

#Day28 Analyses
##Data manipulation
```{r Day28 Data Manipulation}
d1.d28 <- filter(d1, experiment.day == "28" & mesocosm != "28")
str(d1.d28)

##CHANGE IN LEAF NUMBER
d1.d28.leaf.no <- merge(d1.d28, d0, all.x = TRUE, by = c("vase", "exp.leaf.no"))
d1.d28.leaf.no <- subset(d1.d28.leaf.no, select = c(vase:shoot.ID, lesion.pc.y, length.cm.y, no.leaves.y, lesion.presence.y))
str(d1.d28.leaf.no)
d1.d28.leaves = d1.d28.leaf.no %>%
  filter(no.leaves.y != "NA") %>%
  group_by(mesocosm.x, infection.x, site.x, shoot.ID) %>%
  summarize(no.leaves.x = mean(no.leaves.x), no.leaves.y = mean(no.leaves.y), no.leaves.new = mean(no.leaves.new), no.leaves.lost = mean(no.leaves.lost))

d1.d28.leaves$delta.no.leaves <- d1.d28.leaves$no.leaves.x - d1.d28.leaves$no.leaves.y

## LEAF GROWTH
d5 <- subset(d1.d5, select = c(vase:exp.leaf.no, lesion.pc.x, delta.sheath.length, std.length.cm, lesion.presence.x, lesion.absence.x))

d1.d28 <- merge(d1.d28, d0, all.x = TRUE, by = c("vase", "exp.leaf.no"))
d1.d28 <- subset(d1.d28, select = c(vase:shoot.ID, lesion.pc.y:lesion.absence.y))

colnames(d1.d28)[13:15] <- c("length.cm.d28", "area.cm.d28", "lesion.area.d28")
colnames(d1.d28)[17:20] <- c("lesion.pc.d28", "lesion.presence.d28", "lesion.absence.d28", "no.leaves.d28")
colnames(d1.d28)[25] <- "delta.sheath.length.d28"
colnames(d1.d28)[29:33] <- c("lesion.pc.d0", "length.cm.d0", "no.leaves.d0", "lesion.presence.d0", "lesion.absence.d0")

d1.d28 <- merge(d1.d28, d5, all.x = TRUE, by = c("vase", "exp.leaf.no"))

colnames(d1.d28)[34:38] <- c("lesion.pc.d5", "delta.sheath.length.d5", "std.length.cm.d5", "lesion.presence.d5", "lesion.abseence.d5")

d1.d28$delta.sheath.length.d28[is.na(d1.d28$delta.sheath.length.d28)] <-0
d1.d28$delta.sheath.length.d5[is.na(d1.d28$delta.sheath.length.d5)] <- 0

  ###TOTAL GROWTH
d1.d28$delta.sheath.length.total <- d1.d28$delta.sheath.length.d5 + d1.d28$delta.sheath.length.d28
d1.d28$std.length.cm.total <- d1.d28$length.cm.d28 - d1.d28$delta.sheath.length.total

d1.d28.leaf.growth.total <- subset(d1.d28, select = c(vase:current.leaf.no, shoot.ID, std.length.cm.total, length.cm.d0))
d1.d28.leaf.growth.total <- filter(d1.d28.leaf.growth.total, std.length.cm.total != "NA" & length.cm.d0 != "NA")

d1.d28.leaf.growth.total$delta.length.cm <- d1.d28.leaf.growth.total$std.length.cm.total - d1.d28.leaf.growth.total$length.cm.d0


    ####Leaf growth total effect size leaf 1
d1.d28.L1.total.ef <- filter(d1.d28.leaf.growth.total, exp.leaf.no == "1")

d1.d28.L1.total.ef.mean <- aggregate(delta.length.cm ~ infection.x*site.x, FUN = mean, data = d1.d28.L1.total.ef)

d1.d28.L1.total.ef <- filter(d1.d28.L1.total.ef, infection.x == "Y")

d1.d28.L1.total.ef.DC <- filter(d1.d28.L1.total.ef, site.x == "DC")
d1.d28.L1.total.ef.DC$growth.ef <- (d1.d28.L1.total.ef.DC$delta.length.cm - 11.885909)/11.885909

d1.d28.L1.total.ef.LP <- filter(d1.d28.L1.total.ef, site.x == "LP")
d1.d28.L1.total.ef.LP$growth.ef <- (d1.d28.L1.total.ef.LP$delta.length.cm - 9.808545)/9.808545

d1.d28.L1.total.ef.NB <- filter(d1.d28.L1.total.ef, site.x == "NB")
d1.d28.L1.total.ef.NB$growth.ef <- (d1.d28.L1.total.ef.NB$delta.length.cm - 10.861545)/10.861545

d1.d28.L1.total.ef.WB <- filter(d1.d28.L1.total.ef, site.x == "WB")
d1.d28.L1.total.ef.WB$growth.ef <- (d1.d28.L1.total.ef.WB$delta.length.cm - 7.181091)/7.181091

d1.d28.L1.total.ef <- rbind(d1.d28.L1.total.ef.DC, d1.d28.L1.total.ef.LP, d1.d28.L1.total.ef.NB, d1.d28.L1.total.ef.WB)

d1.d28.L1.total.ef.fig <- d1.d28.L1.total.ef %>%
  group_by(site.x) %>%
  summarize(mean.ef = mean(growth.ef), CI.ef = 1.96*se(growth.ef))

  ###GROWTH SINCE DAY 5
d1.d28$std.length.cm.d5d28 <- d1.d28$length.cm.d28 - d1.d28$delta.sheath.length.d28

d1.d28.leaf.growth.d5d28 <- subset(d1.d28, select = c(vase:current.leaf.no, shoot.ID, std.length.cm.d5d28, std.length.cm.d5))
d1.d28.leaf.growth.d5d28 <- filter(d1.d28.leaf.growth.d5d28, std.length.cm.d5d28 != "NA" & std.length.cm.d5 != "NA")

d1.d28.leaf.growth.d5d28$delta.length.cm <- d1.d28.leaf.growth.d5d28$std.length.cm.d5d28 - d1.d28.leaf.growth.d5d28$std.length.cm.d5

#Total growth effect size day28
d1.d28.ef <- d1.d28.leaf.growth.total %>%
  filter(infection.x == "N") %>%
  filter(exp.leaf.no != "4" & exp.leaf.no != "5") %>%
  group_by(exp.leaf.no) %>%
  summarize(control.growth28 = mean(delta.length.cm, na.rm = T))

d28.ef <- merge(d1.d28.leaf.growth.total, d1.d28.ef, by = c("exp.leaf.no"), all.x = T)

d28.ef <- d28.ef %>%
  filter(infection.x == "Y") %>%
  filter(exp.leaf.no != "4" & exp.leaf.no != "5") %>%
  subset(select = c(exp.leaf.no, mesocosm.x, delta.length.cm, control.growth28))

d28.ef$growth.ef <- (d28.ef$delta.length.cm - d28.ef$control.growth28)/d28.ef$control.growth28

#growth fig day 28
d28.ef.fig <- d28.ef %>%
  filter(exp.leaf.no != "0") %>%
  group_by(exp.leaf.no) %>%
  summarize(growth.ef.mean = mean(growth.ef, na.rm = T), growth.ef.95ci = 1.96*se(growth.ef))

#growth since day 5 effect size
d5.d28.ef <- d1.d28.leaf.growth.d5d28 %>%
  filter(infection.x == "N") %>%
  filter(exp.leaf.no != "4" & exp.leaf.no != "5") %>%
  group_by(exp.leaf.no) %>%
  summarize(control.growth528 = mean(delta.length.cm, na.rm = T))

d528.ef <- merge(d1.d28.leaf.growth.d5d28, d5.d28.ef, by = c("exp.leaf.no"), all.x = T)

d528.ef <- d528.ef %>%
  filter(infection.x == "Y") %>%
  filter(exp.leaf.no != "4" & exp.leaf.no != "5") %>%
  subset(select = c(exp.leaf.no, mesocosm.x, delta.length.cm, control.growth528))

d528.ef$growth.ef <- (d528.ef$delta.length.cm - d528.ef$control.growth528)/d528.ef$control.growth528

#growth since day 5 fig day 28
d528.ef.fig <- d528.ef %>%
  group_by(exp.leaf.no) %>%
  summarize(growth.ef.mean = mean(growth.ef, na.rm = T), growth.ef.95ci = 1.96*se(growth.ef))

#growth figure combined day0-28 and day5-28

#d28.ef.1 <-filter(d28.ef, exp.leaf.no == "1")
#d28.ef.1$control.growth28 <- d28.ef.1$control.growth28 + 5.493182
#d28.ef.1$delta.length.cm <- d28.ef.1$delta.length.cm +5.493182
#d28.ef.1$growth.ef <- (d28.ef.1$delta.length.cm - d28.ef.1$control.growth28)/d28.ef.1$control.growth28

#d28.ef.2 <-filter(d28.ef, exp.leaf.no == "2")
#d28.ef.2$control.growth28 <- d28.ef.2$control.growth28 +  12.57829
#d28.ef.2$delta.length.cm <- d28.ef.2$delta.length.cm +  12.57829
#d28.ef.2$growth.ef <- (d28.ef.2$delta.length.cm - d28.ef.2$control.growth28)/d28.ef.2$control.growth28

#d28.ef.3 <-filter(d28.ef, exp.leaf.no == "3")
#d28.ef.3$control.growth28 <- d28.ef.3$control.growth28 + 14.45502
#d28.ef.3$delta.length.cm <- d28.ef.3$delta.length.cm + 14.45502
#d28.ef.3$growth.ef <- (d28.ef.3$delta.length.cm - d28.ef.3$control.growth28)/d28.ef.3$control.growth28

#d28.ef <- rbind(d28.ef.1, d28.ef.2, d28.ef.3)

#growth fig day 28
#d28.ef.fig <- d28.ef %>%
 # filter(exp.leaf.no != "0") %>%
  #group_by(exp.leaf.no) %>%
  #summarize(growth.ef.mean = mean(growth.ef, na.rm = T), growth.ef.95ci = 1.96*se(growth.ef))

d28.ef.fig <- rbind(d528.ef.fig[1,], d28.ef.fig)


####################################################

##BIOMASS AND RHIZOME LENGTH
  ###biomass (d.28)
d1.shoot$b.t.d28 <- d1.shoot$a.g.d28 + d1.shoot$b.g.d28

d1.shoot <- filter(d1.shoot, mesocosm != "28")

d1.shoot$rhizome.growth <- d1.shoot$rhizome.length.cm.D28 - d1.shoot$rhizome.length.cm.D0

  ###Total Biomass effect size
      #### (mean control[split by site] - individual infected)/ mean control [split by site]
d1.shoot.mean.tb <- aggregate(b.t.d28 ~ site + infection, FUN = mean, data = d1.shoot)

d1.shoot.ef.tb.DC <- subset(d1.shoot, site == "DC")
d1.shoot.ef.tb.LP <- subset(d1.shoot, site == "LP")
d1.shoot.ef.tb.NB <- subset(d1.shoot, site == "NB")
d1.shoot.ef.tb.WB <- subset(d1.shoot, site == "WB")

d1.shoot.ef.tb.DC$tb.ef <- (0.5315455 - d1.shoot.ef.tb.DC$b.t.d28)/0.5315455
d1.shoot.ef.tb.LP$tb.ef <- (0.3527273 - d1.shoot.ef.tb.LP$b.t.d28)/0.3527273
d1.shoot.ef.tb.NB$tb.ef <- (0.4861818- d1.shoot.ef.tb.NB$b.t.d28)/0.4861818
d1.shoot.ef.tb.WB$tb.ef <- (0.6234545 - d1.shoot.ef.tb.WB$b.t.d28)/0.6234545

d1.shoot.ef.tb <- rbind(d1.shoot.ef.tb.DC, d1.shoot.ef.tb.LP, d1.shoot.ef.tb.NB, d1.shoot.ef.tb.WB)

d1.shoot.ef.tb <-subset(d1.shoot.ef.tb, infection == "Y")

  ###Rhizome length effect size
    #### (mean control[split by site] - individual infected)/ mean control [split by site]
d1.shoot.mean.si <- aggregate(rhizome.growth ~ site + infection, FUN = mean, data = d1.shoot)

d1.shoot.ef.rhiz.DC <- subset(d1.shoot, site == "DC")
d1.shoot.ef.rhiz.LP <- subset(d1.shoot, site == "LP")
d1.shoot.ef.rhiz.NB <- subset(d1.shoot, site == "NB")
d1.shoot.ef.rhiz.WB <- subset(d1.shoot, site == "WB")

d1.shoot.ef.rhiz.DC$growth.ef <- (1.863636 - d1.shoot.ef.rhiz.DC$rhizome.growth)/1.863636
d1.shoot.ef.rhiz.LP$growth.ef <- (3.363636 - d1.shoot.ef.rhiz.LP$rhizome.growth)/3.363636
d1.shoot.ef.rhiz.NB$growth.ef <- (4.454545 - d1.shoot.ef.rhiz.NB$rhizome.growth)/4.454545
d1.shoot.ef.rhiz.WB$growth.ef <- (2.454545 - d1.shoot.ef.rhiz.WB$rhizome.growth)/2.454545

d1.shoot.ef.rhiz <- rbind(d1.shoot.ef.rhiz.DC, d1.shoot.ef.rhiz.LP, d1.shoot.ef.rhiz.NB, d1.shoot.ef.rhiz.WB)

d1.shoot.ef.rhiz <-subset(d1.shoot.ef.rhiz, infection == "Y")
```

##Lesion Spread Figures and Analyes
```{r Day28 Lesion Presence}
#Figures (*Only infected)
 ##Infection proportion ~ leaf.no
bargraph.CI(x.factor = exp.leaf.no, response = lesion.presence, data = d1.d28.disease, ylim = c(0,1.1), ylab = "Proportion of leaves with lesions", xlab = "exp.leaf.no")

  ##Infected proportion ~ site * leaf.no
bargraph.CI(x.factor = site, group = exp.leaf.no, response = lesion.presence, data = d1.d28.disease, ylim = c(0,5), ylab = "Proportion of leaves with lesions", xlab = "Site", legend = T)

#Analyses (ASK TORRIE FOR GLM)
```

##Lesion Percent Cover Figures and Analyses
```{r Day28 Lesion Percent Cover}
#Figures

  ##Lesion Percent Cover ~ Infection * Leaf.no,
bargraph.CI(x.factor = exp.leaf.no, group = infection.x, response = lesion.pc.d28, data = d1.d28, ylim = c(0,100), ylab = "Lesion percent cover", xlab = "Leaf number", legend = T)

 ###Lesion percent cover ~ infection treatment * leaf.no (*all leaves, excluding dehisced/senesced leaves)
par(mfrow = c(2,2))
bargraph.CI(x.factor = exp.leaf.no, group = infection.x, response = lesion.pc.d28, data = filter(d1.d28, site.x == "DC" & dehisced.senesced == "N"), ylim = c(0,100), ylab = "Lesion percent cover", xlab = "Leaf number", legend = T) ##DC plot
bargraph.CI(x.factor = exp.leaf.no, group = infection.x, response = lesion.pc.d28, data = filter(d1.d28, site.x == "LP" & dehisced.senesced == "N"), ylim = c(0,100), ylab = "Lesion percent cover", xlab = "Leaf number", legend = T) ##LP plot
bargraph.CI(x.factor = exp.leaf.no, group = infection.x, response = lesion.pc.d28, data = filter(d1.d28, site.x == "NB" & dehisced.senesced == "N"), ylim = c(0,100), ylab = "Lesion percent cover", xlab = "Leaf number", legend = T) ##NB plot
bargraph.CI(x.factor = exp.leaf.no, group = infection.x, response = lesion.pc.d28, data = filter(d1.d28, site.x == "WB" & dehisced.senesced == "N"), ylim = c(0,100), ylab = "Lesion percent cover", xlab = "Leaf number", legend = T) ##WB plot

#Analyses
model.lesion.pc.d28 <- lmer(lesion.pc.d28 ~ infection.x*site.x*exp.leaf.no + (1|shoot.ID) + (1|mesocosm.x), data = filter(d1.d28, dehisced.senesced == "N"))
anova(model.lesion.pc.d28) ##Significant interaction: infection*leaf number, lesion.pc.d0 not significant so dropped from model, marginal 3 way interaction between infection*site*leaf number
```

##Leaf Growth Figures and Analyses
```{r Day28 Leaf Growth}
#Total leaf growth
  ##FIGURES
    ###growth effect size
fig.growth <- barplot(c(0,0,0,0), names = d28.ef.fig$exp.leaf.no , ylim = c(-2, 2),
                  ylab = "Effect size of disease on leaf growth",
                  xlab = "Leaf number")
points(x = fig.growth, d28.ef.fig$growth.ef.mean)
arrows(y0 = d28.ef.fig$growth.ef.mean[1:4] - d28.ef.fig$growth.ef.95ci[1:4], y1 = d28.ef.fig$growth.ef.mean[1:4] + d28.ef.fig$growth.ef.95ci[1:4], x0 = fig.growth, x1 =fig.growth, angle = 90, code = 3, #95% CI
length = 0.1)

  ###Leaf 1 growth effect size by site
fig.growth <- barplot(c(0,0,0,0), names = d1.d28.L1.total.ef.fig$site.x , ylim = c(-1, 1),
                  ylab = "Effect size of disease on leaf 1 growth",
                  xlab = "Site")
points(x = fig.growth, d1.d28.L1.total.ef.fig$mean.ef)
arrows(y0 = d1.d28.L1.total.ef.fig$mean.ef[1:4] - d1.d28.L1.total.ef.fig$CI.ef[1:4], y1 = d1.d28.L1.total.ef.fig$mean.ef[1:4] + d1.d28.L1.total.ef.fig$CI.ef[1:4], x0 = fig.growth, x1 =fig.growth, angle = 90, code = 3, #95% CI
length = 0.1)

  ##Leaf 1 growth effect size one-sample t-test
fig.growth <- barplot(c(0), ylim = c(-1, 1),
                  ylab = "Effect size of disease on leaf 1 growth")
points(x = fig.growth, mean(d1.d28.L1.total.ef$growth.ef))
arrows(y0 = mean(d1.d28.L1.total.ef$growth.ef)- 1.96*se(d1.d28.L1.total.ef$growth.ef), y1 = mean(d1.d28.L1.total.ef$growth.ef) + 1.96*se(d1.d28.L1.total.ef$growth.ef), x0 = fig.growth, x1 =fig.growth, angle = 90, code = 3, #95% CI
length = 0.1)


    ###Growth ~ infection treatment * leaf.no
bargraph.CI(x.factor = exp.leaf.no, group = infection.x, response = delta.length.cm, data = filter(d1.d28.leaf.growth.total, exp.leaf.no != "4" & exp.leaf.no != "5"), ylim = c(0,15), ylab = "Leaf growth (cm)", xlab = "Leaf number", legend = T)

    ###Growth ~ site * leaf.no 
bargraph.CI(x.factor = exp.leaf.no, group = site.x, response = delta.length.cm, data = filter(d1.d28.leaf.growth.total, exp.leaf.no != "4" & exp.leaf.no != "5"), ylim = c(0,15), ylab = "Leaf growth (cm)", xlab = "Leaf number", legend = T)

  ##Analyses
model.growth.std.total <- lmer(std.length.cm.total ~ infection.x*site.x*exp.leaf.no + (1|shoot.ID) + (1|mesocosm.x) + length.cm.d0, data = filter(d1.d28.leaf.growth.total, exp.leaf.no != "4" & exp.leaf.no != "5")) #adjusting for delta sheath length 
anova(model.growth.std.total) #Significant interactions: site*leaf number and Infection*leaf number (Excluded leaves 4 and 5 because not enough reps)

    ####Only leaf 1
model.growth.std.d28.L1 <- lmer(std.length.cm.total ~ infection.x*site.x + (1|mesocosm.x) + length.cm.d0, data = filter(d1.d28.leaf.growth.total, exp.leaf.no == "1")) #adjusting for delta sheath length 
anova(model.growth.std.d28.L1)

    ####Effect size
model.L1.ef.total <- lmer(growth.ef ~ site.x +(1|mesocosm.x), data = d1.d28.L1.total.ef)
anova(model.L1.ef.total)

t.test(d1.d28.L1.total.ef$growth.ef, mu = 0)

#Day5-Day28 leaf growth
  ##FIGURES
    ###Growth effect size
fig.growth <- barplot(c(0,0,0), names = d528.ef.fig$exp.leaf.no[1:3] , ylim = c(-1, 1),
                  ylab = "Effect size of disease on leaf growth d5-28",
                  xlab = "Leaf number")
points(x = fig.growth, d528.ef.fig$growth.ef.mean[1:3])
arrows(y0 = d528.ef.fig$growth.ef.mean[1:3] - d528.ef.fig$growth.ef.95ci[1:3], y1 = d528.ef.fig$growth.ef.mean[1:3] + d528.ef.fig$growth.ef.95ci[1:3], x0 = fig.growth, x1 =fig.growth, angle = 90, code = 3, #95% CI
length = 0.1)

    ###Growth ~ infection treatment * leaf.no
bargraph.CI(x.factor = exp.leaf.no, group = infection.x, response = delta.length.cm, data = filter(d1.d28.leaf.growth.d5d28, exp.leaf.no != "4" & exp.leaf.no != "5"), ylim = c(0,20), ylab = "Leaf growth (cm)", xlab = "Leaf number", legend = T)

    ###Growth ~ site * leaf.no 
bargraph.CI(x.factor = exp.leaf.no, group = site.x, response = delta.length.cm, data = filter(d1.d28.leaf.growth.d5d28, exp.leaf.no != "4" & exp.leaf.no != "5"), ylim = c(0,25), ylab = "Leaf growth (cm)", xlab = "Leaf number", legend = T)

  ##Analyses
model.growth.std.d5d28 <- lmer(std.length.cm.d5d28 ~ infection.x*site.x*exp.leaf.no + (1|shoot.ID) + (1|mesocosm.x) + std.length.cm.d5, data = filter(d1.d28.leaf.growth.d5d28, exp.leaf.no != "4" & exp.leaf.no != "5")) #adjusting for delta sheath length 
anova(model.growth.std.d5d28) #Significant interactions: site*leaf number and Infection*leaf number (Excluded leaves 4 and 5 because not enough reps)

    ### Only leaf 0
model.growth.std.d5d28.L1 <- lmer(std.length.cm.d5d28 ~ infection.x*site.x + (1|mesocosm.x) + std.length.cm.d5, data = filter(d1.d28.leaf.growth.d5d28, exp.leaf.no == "0")) #adjusting for delta sheath length 
anova(model.growth.std.d5d28.L1) #Significant interactions: site*leaf number and Infection*leaf number (Excluded leaves 4 and 5 because not enough reps)
```


##Change in leaf number Figures and Analyses
```{r Day28 Leaf Number}
#Figures

  ##Change in leaves ~ site*infection
bargraph.CI(x.factor = site.x, group = infection.x, response = delta.no.leaves, data = d1.d28.leaves, ylim = c(-2,2), ylab = "Change in the number of leaves per shoot", xlab = "Site", legend = T)

  ##Change in leaves ~ infection
bargraph.CI(x.factor = infection.x, response = delta.no.leaves, data = d1.d28.leaves, ylim = c(-2,2), ylab = "Change in the number of leaves per shoot", xlab = "Infection")

  ##Change in leaves ~ site
bargraph.CI(x.factor = site.x, response = delta.no.leaves, data = d1.d28.leaves, ylim = c(-2,2), ylab = "Change in the number of leaves per shoot", xlab = "Infection")

  ##Number of leaves produced ~ infection
  bargraph.CI(x.factor = infection.x, response = no.leaves.new, data = d1.d28.leaves, ylim = c(0, 3), ylab = "Number of leaves produced per shoot", xlab = "Infection")

  ##Number of leaves lost ~ site * infection
  bargraph.CI(x.factor = site.x, group = infection.x, response = no.leaves.lost, data = d1.d28.leaves, ylim = c(0, 3), ylab = "Number of leaves lost per shoot", xlab = "Site", legend = T)
  
  
#Analyses
model.no.leaves.d28 <- lmer(no.leaves.x ~ infection.x*site.x + (1|mesocosm.x) + no.leaves.y , data = d1.d28.leaves)
anova(model.no.leaves.d28) #Significant main effets of infection and site, marginally significant interaction between site and infection

model.new.leaves.d28 <- lmer(no.leaves.new ~ infection.x*site.x + (1|mesocosm.x) + no.leaves.y, data = d1.d28.leaves)
anova(model.new.leaves.d28) #Significant Main effect of infection 

model.leaves.lost.d28 <- lmer(no.leaves.lost ~ infection.x*site.x + (1|mesocosm.x) + no.leaves.y, data = d1.d28.leaves)
anova(model.leaves.lost.d28) # Significant interaction between infection and site
```

## Biomass Figures and Analysis
```{r Day28 Biomass}
#Figures
  ##Effect Size
    ###Effect Size ~ Infection x site
bargraph.CI(x.factor = site, response = tb.ef, data = d1.shoot.ef.tb, ylim = c(0,1), ylab = "Proportion Biomass reduction in disease plants over 28 days", xlab = "Site", legend = TRUE)

  ##Raw Data
    ##Total biomass: infection x site
bargraph.CI(x.factor = site, group = infection, response = b.t.d28, data = d1.shoot, ylab = "Total biomass (g)", xlab = "Site", ylim = c(0,1), legend = TRUE)

    ##above-ground: infection x site
bargraph.CI(x.factor = site, group = infection, response = a.g.d28, data = d1.shoot, ylab = "Above-ground biomass (g)", xlab = "Site", ylim = c(0,0.7), col = c("darkgreen", "brown"))
legend(x= "topright", legend = c("Control", "Infected"), fill = c("darkgreen", "brown"))

    ##below-ground: infection x site
bargraph.CI(x.factor = site, group = infection, response = b.g.d28, data = d1.shoot, ylab = "Below-ground biomass (g)", xlab = "Site", ylim = c(0,0.4), col = c("darkgreen", "brown"))
legend(x= "topright", legend = c("Control", "Infected"), fill = c("darkgreen", "brown"))

#Analyses
  ##Effect Size
model.biomass.tb.ef <- lmer(tb.ef ~ site + (1|mesocosm), data = d1.shoot.ef.tb)
anova(model.biomass.tb.ef)

summary(glht(model.biomass.tb.ef,linfct = mcp(site = "Tukey")))

  ##Raw Data
    ###total biomass
model.biomass.A <- lmer(b.t.d28 ~ infection * site + (1|mesocosm), data = d1.shoot)
anova(model.biomass.A)

    ###above-ground biomass
model.biomass.B <- lmer(a.g.d28 ~ infection * site + (1|mesocosm), data = d1.shoot)
anova(model.biomass.B)

    ###below-ground biomass
model.biomass.C <- lmer(b.g.d28 ~ infection * site + (1|mesocosm), data = d1.shoot)
anova(model.biomass.C)
```


##Rhizome Figures and Analyses
```{r Day28 Rhizome Growth}
#Figures
  ##Effect Size
    ###Effect Size ~ Infection x site
bargraph.CI(x.factor = site, response = growth.ef, data = d1.shoot.ef.rhiz, ylim = c(0,1.5), ylab = "Proportion rhizome growth reduction in disease plants over 28 days", xlab = "Site", legend = TRUE)

  ##Raw data
    ##chance in rhizome length ~ infection * site
bargraph.CI(x.factor = site, group = infection, response = rhizome.length.cm.D28-rhizome.length.cm.D0, data = filter(d1.shoot, rhizome.length.cm.D0 != "NA"), ylim = c(0,8), ylab = "Rhizome growth (cm)", xlab = "Site", legend = TRUE)

#Analyses
  ##Effect Size
model.rhizome.growth.ef <- lmer(growth.ef ~ site + (1|mesocosm), data = d1.shoot.ef.rhiz)
anova(model.rhizome.growth.ef)

summary(glht(model.rhizome.growth.ef,linfct = mcp(site = "Tukey")))

  ##Raw data
model.rhizome.growth <- lmer(rhizome.length.cm.D28 ~ infection * site + (1|mesocosm), data = filter(d1.shoot, rhizome.length.cm.D0 != "NA"))
anova(model.rhizome.growth) #mesocosm not significant so removed from the model
```

##Home VS. Away

###Data management
```{r Day28 Home vs. Away Data Management}

d1.shoot.ef.tb$hva <- NA
d1.shoot.ef.tb$hva[d1.shoot.ef.tb$site == "DC"] <- "home"
d1.shoot.ef.tb$hva[d1.shoot.ef.tb$site == "LP"] <- "away"
d1.shoot.ef.tb$hva[d1.shoot.ef.tb$site == "NB"] <- "away"
d1.shoot.ef.tb$hva[d1.shoot.ef.tb$site == "WB"] <- "away"

d1.shoot$hva <- NA
d1.shoot$hva[d1.shoot$site == "DC"] <- "home"
d1.shoot$hva[d1.shoot$site == "LP"] <- "away"
d1.shoot$hva[d1.shoot$site == "NB"] <- "away"
d1.shoot$hva[d1.shoot$site == "WB"] <- "away"

```

###Biomass Figures and Analysis
```{r Day28 Home vs. Away Biomass}
#Figures
  ##Effect Size
    ###Effect Size ~ Infection x site
bargraph.CI(x.factor = hva, response = tb.ef, data = d1.shoot.ef.tb, ylim = c(0,1), ylab = "Proportion Total Biomass reduction in disease plants over 28 days", xlab = "Location", legend = TRUE)

  ##Raw Data
    ##Total biomass: infection x site
bargraph.CI(x.factor = hva, group = infection, response = b.t.d28, data = d1.shoot, ylab = "Total biomass (g)", xlab = "Location", ylim = c(0,1), legend = TRUE)

    ##above-ground: infection x site
bargraph.CI(x.factor = hva, group = infection, response = a.g.d28, data = d1.shoot, ylab = "Above-ground biomass (g)", xlab = "Location", ylim = c(0,0.7), col = c("grey90", "black"))
legend(x= "topright", legend = c("Control", "Infected"), fill = c("grey90", "black"))

    ##below-ground: infection x site
bargraph.CI(x.factor = hva, group = infection, response = b.g.d28, data = d1.shoot, ylab = "Below-ground biomass (g)", xlab = "Location", ylim = c(0,0.4), col = c("grey90", "black"))
legend(x= "topright", legend = c("Control", "Infected"), fill = c("grey90", "black"))

#Analyses
  ##Effect Size
model.biomass.tb.ef.hva <- lmer(tb.ef ~ hva + (1|site) + (1|mesocosm), data = d1.shoot.ef.tb)
anova(model.biomass.tb.ef.hva)

  ##Raw Data
    ###total biomass
model.biomass.A <- lmer(b.t.d28 ~ infection * hva + (1|site) + (1|mesocosm), data = d1.shoot)
anova(model.biomass.A)

    ###above-ground biomass
model.biomass.B <- lmer(a.g.d28 ~ infection * hva + (1|site) + (1|mesocosm), data = d1.shoot)
anova(model.biomass.B)

    ###below-ground biomass
model.biomass.C <- lmer(b.g.d28 ~ infection * hva + (1|site) + (1|mesocosm), data = d1.shoot)
anova(model.biomass.C)
```

#Environment Analysis
##Data manipulation
```{r Environment Data manipulation}
d1.env$mesocosm <- as.factor(d1.env$mesocosm)

str(d1.env)

d1.env.summary = d1.env %>%
  group_by(day, experiment.day, infection) %>%
  summarize(mean.T = mean(Temperature.C), sd.T = sd(Temperature.C), mean.S = mean(Salinity.ppt), sd.S = 1.96*sd(Salinity.ppt))

str(d1.env.summary)

d1.env.summary.I <- subset(d1.env.summary, infection == "Y")
d1.env.summary.C <- subset(d1.env.summary, infection == "N")
d1.env.summary.F <- subset(d1.env.summary, infection == "DC")
```

## Temperature Figures and Analyses
```{r Temperature}
#Full summer figures
plot(dfull.env$sample.no, dfull.env$Temp.C,
     ylim = range(c(5, 25)),
     pch = 19,
     cex = .25,
     xlab = "Day",
     ylab = "Temperature (C)")


#Figures
plot(d1.env.summary.F$day, d1.env.summary.F$mean.T,
     ylim = range(c(10,25)),
     pch = 19, col = "blue",
     xlab = "Day of August", ylab = "Temperature (C)")

arrows(d1.env.summary.F$day, d1.env.summary.F$mean.T - d1.env.summary.F$sd.T, d1.env.summary.F$day, d1.env.summary.F$mean.T + d1.env.summary.F$sd.T, length = 0.05, angle = 90, code = 3, col = "blue")

points(d1.env.summary.C$day, d1.env.summary.C$mean.T,
     pch = 1, xlab = "Day of August", ylab = "Temperature (C)")

arrows(d1.env.summary.C$day, d1.env.summary.C$mean.T - d1.env.summary.C$sd.T, d1.env.summary.C$day, d1.env.summary.C$mean.T + d1.env.summary.C$sd.T, length = 0.05, angle = 90, code = 3)

points(d1.env.summary.I$day, d1.env.summary.I$mean.T,
     pch = 19, xlab = "Day of August", ylab = "Temperature (C)")

arrows(d1.env.summary.I$day, d1.env.summary.I$mean.T - d1.env.summary.I$sd.T, d1.env.summary.I$day, d1.env.summary.I$mean.T + d1.env.summary.I$sd.T, length = 0.05, angle = 90, code = 3)

#Analyses

```

## Salinity Figures and Analyses
```{r Salinity}
#Figures
plot(d1.env.summary.I$day, d1.env.summary.I$mean.S,
     ylim = range(c(30,34)),
     pch = 19,
     xlab = "Day of August", ylab = "Salinty (ppt)")

arrows(d1.env.summary.I$day, d1.env.summary.I$mean.S - d1.env.summary.I$sd.S, d1.env.summary.I$day, d1.env.summary.I$mean.S + d1.env.summary.I$sd.S, length = 0.05, angle = 90, code = 3)

points(d1.env.summary.C$day, d1.env.summary.C$mean.S,
     pch = 1, xlab = "Day of August", ylab = "Salinity (ppt)")

arrows(d1.env.summary.C$day, d1.env.summary.C$mean.S - d1.env.summary.C$sd.S, d1.env.summary.C$day, d1.env.summary.C$mean.S + d1.env.summary.C$sd.S, length = 0.05, angle = 90, code = 3)
```


#Field Data
##Data manipulation
```{r Field Data Manipulation}
str(d1.field)
d1.field$quad <- as.factor(d1.field$quad)

#means by quad
d1.field.quad <- d1.field %>%
  group_by(site, quad) %>%
  summarize(mean.length = mean(length.cm, na.rm = T), mean.leaves = mean(no.leaves, na.rm = T), mean.lp = mean(lesion.present, na.rm = T), no.shoots = mean(no.shoots))

#means by site
d1.field.site <- d1.field %>%
  group_by(site) %>%
  summarize(mean.lp = mean(lesion.present, na.rm = T))

#mean severity by quad
d1.field.severity <- filter(d1.field, lesion.pc.2 > 0)
d1.field.qs <- d1.field.severity %>%
  group_by(site,quad) %>%
  summarize(mean.lpc = mean(lesion.pc.2))

#master mean data by quad
d1.field.quad <- merge(d1.field.quad, d1.field.qs, all.x = T)
```

##Figures
```{r FieldFigures}
#Site * Length
bargraph.CI(x.factor = site, response = mean.length, data = d1.field.quad, ylab = "Length (cm)", xlab = "Site", ylim = c(0,150))

#Site * Leaf number
bargraph.CI(x.factor = site, response = mean.leaves, data = d1.field.quad, ylab = "Leaf number", xlab = "Site", ylim = c(0,6))

#Site * shoot number
bargraph.CI(x.factor = site, response = no.shoots, data = d1.field.quad, ylab = "shoot number", xlab = "Site", ylim = c(0,40))

#Site * lesion prevalence
bargraph.CI(x.factor = site, response = mean.lp, data = d1.field.quad, ylab = "Proportion infected", xlab = "Site", ylim = c(0,1))

#Site * lesion percent cover
bargraph.CI(x.factor = site, response = mean.lpc, data = d1.field.quad, ylab = "Lesion percent cover", xlab = "Site", ylim = c(0,15))

#lesion prevalence * Length
plot(mean.lp ~ mean.length, data = d1.field.quad)

plot(mean.lp ~ mean.length, data = subset(d1.field.quad, site == "DC"), ylim = c(0,1), xlim = c(35,120))
points(mean.lp ~ mean.length, data = subset(d1.field.quad, site == "LP"), col = "blue")
points(mean.lp ~ mean.length, data = subset(d1.field.quad, site == "WB"), col = "red")
points(mean.lp ~ mean.length, data = subset(d1.field.quad, site == "NB"), col = "orange")

#lesion.prevalence * leaf number
plot(mean.lp ~ mean.leaves, data = d1.field.quad)

#lesion.prevalence * shoot number
plot(mean.lp ~ no.shoots, data = subset(d1.field.quad, site == "DC"), xlim = c(0,70))
points(mean.lp ~ no.shoots, data = subset(d1.field.quad, site == "LP"), col = "blue")
points(mean.lp ~ no.shoots, data = subset(d1.field.quad, site == "WB"), col = "red")
points(mean.lp ~ no.shoots, data = subset(d1.field.quad, site == "NB"), col = "orange")

#Map of sites
setwd("~/Dropbox/EEMB Graduate/Research/ZosteraWastingDisease/Greenhouse_Mesocosm/Innoculation Trials/Trial_2/NE_seagrass_habitat/MassDEP Seagrass (1995 and 2001)")
ogrInfo(".", "GISDATA_EELGRASS_POLY")
zm.95.01 <- readOGR(dsn = ".", layer = "GISDATA_EELGRASS_POLY")   #layer of seagrass habitat MA
#str(zm.95.01)

setwd("~/Dropbox/EEMB Graduate/Research/ZosteraWastingDisease/Greenhouse_Mesocosm/Innoculation Trials/Trial_2/NE_seagrass_habitat/SAV12")
ogrInfo(".", "SAV12")
zm.ri.12 <- readOGR(dsn = ".", layer = "SAV12")   #layer of seagrass habitat RI
data_name <- "zm.ri.12.reproj" #name for new projection
assign(data_name, spTransform(zm.ri.12, CRS("+proj=longlat"))) #reassigning polygons to new projection
plot(zm.ri.12.reproj) #testing plot

setwd("~/Dropbox/EEMB Graduate/Research/ZosteraWastingDisease/Greenhouse_Mesocosm/Innoculation Trials/Trial_2/State Boundaries/MA Boundary")
ogrInfo(".", "GISDATA_OUTLINE25K_ARC")
MA.boundary <- readOGR(dsn = ".", layer = "GISDATA_OUTLINE25K_ARC")   #layer of MA State boundary

setwd("~/Dropbox/EEMB Graduate/Research/ZosteraWastingDisease/Greenhouse_Mesocosm/Innoculation Trials/Trial_2/State Boundaries/RI_CUSP")
ogrInfo(".", "RI_CUSP")
RI.boundary <- readOGR(dsn = ".", layer = "RI_CUSP")   #layer of RI coastline


(setwd("~/Dropbox/EEMB Graduate/Research/ZosteraWastingDisease/Greenhouse_Mesocosm/Innoculation Trials/Trial_2/Analyses/Data for analyses")) ##Returning working direction

#Site figure
map("worldHires", "usa", xlim = c(-71.2,-70.45), ylim = c(42.2, 42.65), col = "white", fill = FALSE)
plot(MA.boundary, add = TRUE, xlim = c(-71.2,-70.45), ylim = c(42.2, 42.65), col = "grey80")
plot(zm.95.01, add = TRUE, xlim = c(-71.2,-70.45), ylim = c(42.2, 42.65), col = "red", border = FALSE)
add.pie(z = c(0.6,0.4), x = -70.81579, y = 42.38063, radius = 0.02, col = c("purple", "white"), labels = "Nahant*", label.dist = 1.25, clockwise = TRUE)
add.pie(z = c(0.29, 0.71), x = -70.80543, y = 42.464487, radius = 0.02, col = c("darkgreen", "white"), labels = "Beverly", label.dist = 1.25, clockwise = TRUE)
add.pie(z = c(0.69, 0.31), x = -70.7309, y = 42.54013, radius = 0.02, col = c("blue", "white"), labels = c("Manchester", ""), label.dist = 1.25, clockwise = TRUE)
add.pie(z = c(0.47, 0.53), x = -70.75592, y = 42.60711, radius = 0.02, col = c("orange", "white"), labels = c("", "Gloucester"), label.dist = 1.25, clockwise = TRUE)
points(-70.91579, 42.42063, pch = "O", col = "purple")
points(-70.85843, 42.54487, pch = "O", col = "darkgreen")
points(-70.80609, 42.55913, pch = "O", col = "blue")
points(-70.65592, 42.59711, pch = "O", col = "orange")
points(-71.05888, 42.36008, pch = 18, col = "Black", cex = 2)
text(-71.02, 42.335, "Boston, MA")
map.scale(-70.637, 42.25, ratio = FALSE)
box(col = "darkblue", lwd = "3")

#seagrass distribution
map("worldHires", "usa", xlim = c(-71.2,-70.45), ylim = c(42.2, 42.65), col = "white", fill = FALSE)
plot(MA.boundary, add = TRUE, xlim = c(-71.2,-70.45), ylim = c(42.2, 42.65), col = "grey80")
plot(zm.95.01, add = TRUE, xlim = c(-71.2,-70.45), ylim = c(42.2, 42.65), col = "red", border = FALSE)
points(-71.05888, 42.36008, pch = 18, col = "Black", cex = 2)
text(-71.02, 42.335, "Boston, MA")
map.scale(-70.63, 42.25, ratio = FALSE)

#Site locations
map("worldHires", "usa", xlim = c(-71.2,-70.45), ylim = c(42.2, 42.65), col = "white", fill = FALSE)
plot(MA.boundary, add = TRUE, xlim = c(-71.2,-70.45), ylim = c(42.2, 42.75), col = "grey80")
points(-70.91579, 42.42063, pch = 17, col = "purple")
points(-70.85843, 42.54487, pch = 17, col = "darkgreen")
points(-70.80609, 42.55913, pch = 17, col = "blue")
points(-70.65592, 42.59711, pch = 17, col = "orange")
points(-71.05888, 42.36008, pch = 18, col = "Black", cex = 2)
text(-70.85, 42.4, "Nahant")
text( -70.92, 42.56, "Beverly")
text(-70.7, 42.55, "Manchester")
text(-70.58, 42.62, "Gloucester")
text(-71.02, 42.335, "Boston, MA")
map.scale(-70.637, 42.25, ratio = FALSE)
box(col = "darkblue", lwd = "3")

#New England seagrass distribution
map('state', region = c('mass', 'rhode island'), col = "white")
map("worldHires", xlim = c(-72,-69), ylim = c(40, 43.00), col = "white", fill = FALSE)
plot(MA.boundary, add = TRUE, xlim = c(-71.2,-69), ylim = c(40, 43), col = "grey80", lwd = 0.25)
plot(RI.boundary, add = TRUE, xlim = c(-72, -71), ylim = c(40, 42.65), col = "grey80", lwd = 0.25)
plot(zm.95.01, add = TRUE, xlim = c(-72.2,-69), ylim = c(40, 43), col = "red", border = FALSE)
plot(zm.ri.12.reproj, add = TRUE, col = "red", border = FALSE)
points(-71.05888, 42.36008, pch = 18, col = "Black", cex = 2)
text(-71.02, 42.335, "Boston, MA")
map.scale(-72, 42, ratio = FALSE)
```

##Dorothy Cove Depth Prevalence analyses/Figures
```{r}

#Test of variation in proportion across depth
disease <- c(21, 53, 72)
healthy <- c(139, 75, 47)
total <- c(160, 128, 119)

prop.test(disease, total)

m.dc.prev <- glm(cbind(lesion.present, lesion.absent) ~ depth, data = d1.dc.field, family = "binomial")
summary(m.dc.prev, test = "LR")

#figure, prevalence
counts <- table(d1.dc.field$lesion.absent, d1.dc.field$depth)
par(las =1, mgp = c(2.5, 0.2, 0), mfrow = c(1,1), mar = c(3.75,4,0.5,0.375), tck = 0.01)
#par(oma = c(2, 1, 1, 1))
op <- par("usr")
barplot(counts,
        ylab = "No. Z. marina shoots", xlab = "Depth",
        legend = c("lesions", "no lesions"),
        args.legend = list(x = "topright", bty = "n", cex = 1.5),
        cex.lab = 2, cex.axis = 1.25,cex.names = 1.25,
        ylim = c(0,200))

#Test severity across depth
m.dc.l.pc <- aov(lesion.pc.2 ~ depth, data = d1.dc.field)
anova(m.dc.l.pc)

TukeyHSD(m.dc.l.pc)

#figure, severity
bargraph.CI(x.factor = depth, response = lesion.pc.2, data = d1.dc.field, ylim = c(0,15), ylab = "Lesion percent cover", xlab = "Depth")


```







































############################################################################################
############################################################################################

#Data manipulation
```{r}
# ###NEED TO FIX THIS AROUND TO INCORPORATE NEW DATA MANAGEMENT STRATEGY 1/11/17 :) :P
# 
# #change per leaf
#   library(dplyr)
# 
# d2 <- select(d1, c(infection, leaf.no, length.cm, mesocosm, site))
# d2$growth <- d2$length.d5 - d2$length.d0
# 
#   ##change new leaf
# d2.new <- filter(d2, leaf.no == "0")
# 
#   ##change leaf 1
# d2.1 <- filter(d2, leaf.no == "1")
# 
#   ##change leaf 2
# d2.2 <- filter(d2, leaf.no == "2")
# 
#   ##change leaf 3
# d2.3 <- filter(d2, leaf.no == "3")
# 
#   ##change leaf 4
# d2.4 <- filter(d2, leaf.no == "4")
# 
# 
# #lesion percent cover
# 
# d3 <- select(d1, c(mesocosm, site, infection, leaf.no, lesion.area.d5, percent.cover.d5))
# 
#   ##lesions leaf 1
# d3.1 <- filter(d3, infection == "Y", leaf.no == "1")
# 
#   ##lesions leaf 2
# d3.2 <- filter(d3, infection == "Y", leaf.no == "2")
# 
#   ##lesions leaf 3
# d3.3 <- filter(d3, infection == "Y", leaf.no == "3")
# 
#   ##mean area and percent cover over leaves 1 and 2
# d3.mean <- aggregate(lesion.area.d5 ~ mesocosm + site + infection, FUN = mean, data = subset(d3, leaf.no == "1" | leaf.no == "2"))
# 
# d3.mean.pc <- aggregate(percent.cover.d5 ~ mesocosm + site + infection, FUN = mean, data = subset(d3, leaf.no == "1" | leaf.no == "2"))
# 
# d3.mean$percent.cover.d5 <- d3.mean.pc$percent.cover.d5
# 
# #change no.leaves
# d4 <- select(d1, c(mesocosm, site, infection, no.leaves.d0, no.leaves.d5, no.leaves.d28, new.leaves.d28, leaves.lost.d28))
# d4$change.leaves.d5 <- d4$no.leaves.d5 - d4$no.leaves.d0
# d4$change.leaves.d28 <- d4$no.leaves.d28 - d4$no.leaves.d0
# d4 <- aggregate(data=d4, cbind(no.leaves.d0, no.leaves.d5, no.leaves.d28, change.leaves.d5, change.leaves.d28, new.leaves.d28, leaves.lost.d28) ~ infection*site*mesocosm, FUN = mean)
# 
# ##Leaf Growth Effect Size
# ###Mean growth by infection and site
# d2.mean.si <- aggregate(growth ~ site + infection + leaf.no, FUN = mean, data = subset(d2, leaf.no == "1" | leaf.no == "2"))
# 
# d2.ef.1 <- subset(d2, leaf.no == "1")
# d2.ef.2 <- subset(d2, leaf.no == "2")
# 
# d2.ef.1.DC <- subset(d2.ef.1, site == "DC")
# d2.ef.1.LP <- subset(d2.ef.1, site == "LP")
# d2.ef.1.NB <- subset(d2.ef.1, site == "NB")
# d2.ef.1.WB <- subset(d2.ef.1, site == "WB")
# d2.ef.2.DC <- subset(d2.ef.2, site == "DC")
# d2.ef.2.LP <- subset(d2.ef.2, site == "LP")
# d2.ef.2.NB <- subset(d2.ef.2, site == "NB")
# d2.ef.2.WB <- subset(d2.ef.2, site == "WB")
# 
# d2.ef.1.DC$growth.ef <- (4.4395455 - d2.ef.1.DC$growth)/4.4395455
# d2.ef.1.LP$growth.ef <- (3.5593636 - d2.ef.1.LP$growth)/3.5593636
# d2.ef.1.NB$growth.ef <- (4.4511818 - d2.ef.1.NB$growth)/4.4511818
# d2.ef.1.WB$growth.ef <- (3.1115455 - d2.ef.1.WB$growth)/3.1115455
# d2.ef.2.DC$growth.ef <- (0.9873636 - d2.ef.2.DC$growth)/0.9873636
# d2.ef.2.LP$growth.ef <- (1.1100000 - d2.ef.2.LP$growth)/1.1100000
# d2.ef.2.NB$growth.ef <- (2.1352727 - d2.ef.2.NB$growth)/2.1352727
# d2.ef.2.WB$growth.ef <- (0.7261000 - d2.ef.2.WB$growth)/0.7261000
# 
# d2.ef <- rbind(d2.ef.1.DC, d2.ef.1.LP, d2.ef.1.NB, d2.ef.1.WB, d2.ef.2.DC, d2.ef.2.LP, d2.ef.2.NB, d2.ef.2.WB)
# 
# d2.ef <-subset(d2.ef, infection == "Y")
# 
# #biomass (d.28)
# d1.shoot$b.t.d28 <- d1.shoot$a.g.d28 + d1.shoot$b.g.d28
# 
# d1.shoot <- filter(d1.shoot, vase != "91", vase != "92")
# 
# d1.shoot$rhizome.growth <- d1.shoot$rhizome.length.cm.D28 - d1.shoot$rhizome.length.cm.D0
# 
# ##Rhizome length effect size
# ### (mean control[split by site] - individual infected)/ mean control [split by site]
# d1.shoot.mean.si <- aggregate(rhizome.growth ~ site + infection, FUN = mean, data = d1.shoot)
# 
# d1.shoot.ef.rhiz.DC <- subset(d1.shoot, site == "DC")
# d1.shoot.ef.rhiz.LP <- subset(d1.shoot, site == "LP")
# d1.shoot.ef.rhiz.NB <- subset(d1.shoot, site == "NB")
# d1.shoot.ef.rhiz.WB <- subset(d1.shoot, site == "WB")
# 
# d1.shoot.ef.rhiz.DC$growth.ef <- (1.863636 - d1.shoot.ef.rhiz.DC$rhizome.growth)/1.863636
# d1.shoot.ef.rhiz.LP$growth.ef <- (3.291667 - d1.shoot.ef.rhiz.LP$rhizome.growth)/3.291667
# d1.shoot.ef.rhiz.NB$growth.ef <- (4.416667 - d1.shoot.ef.rhiz.NB$rhizome.growth)/4.416667
# d1.shoot.ef.rhiz.WB$growth.ef <- (2.333333 - d1.shoot.ef.rhiz.WB$rhizome.growth)/2.333333
# 
# d1.shoot.ef.rhiz <- rbind(d1.shoot.ef.rhiz.DC, d1.shoot.ef.rhiz.LP, d1.shoot.ef.rhiz.NB, d1.shoot.ef.rhiz.WB)
# 
# d1.shoot.ef.rhiz <-subset(d1.shoot.ef.rhiz, infection == "Y")
# ```
# 
# #Length Area Regression
# ```{r}
# model.length.area <- aov(area.cm ~ length.cm*leaf.no*site*infection*experiment.day*clipped, data = d1)
# summary(model.length.area)
# 
# model.length.area <- lm(area.cm ~ length.cm, data = subset(d1, length.cm >= 0 & broken.sheath != "Y"))
# summary(model.length.area)
# 
# plot(area.cm ~ length.cm, ylim = c(0,30), xlim = c(0, 75), data = subset(d1, length.cm >= 0 & broken.sheath != "Y"))
# 
# plot(length.cm ~ area.cm, data = d1, ylim = c(0,75), xlim = c(0,30), col = c("red", "orange", "yellow", "green", "blue", "purple", "black", "brown")[leaf.no])
# legend(x="topright", legend = levels(d1$leaf.no), col=c("red", "orange", "yellow", "green", "blue", "purple", "black", "brown"), pch=1)
# 
#    plot(length.cm ~ area.cm, data = subset(d1, leaf.no == "1"))
# 
# plot(length.cm ~ area.cm, data = d1, ylim = c(0,75), xlim = c(0,30), col = c("red", "yellow", "green", "blue")[site])
# legend(x="topright", legend = levels(d1$site), col=c("red", "yellow", "green", "blue"), pch=1)
# 
# plot(length.cm ~ area.cm, data = d1, ylim = c(0,75), xlim = c(0,30), col = c("green", "brown")[infection])
# legend(x="topright", legend = levels(d1$infection), col=c("green", "brown"), pch=1)
# 
# plot(length.cm ~ area.cm, data = d1, ylim = c(0,75), xlim = c(0,30), col = c("red", "blue", "green")[clipped])
# legend(x="topright", legend = levels(d1$clipped), col=c("red", "blue", "green"), pch=1)
# 
# plot(length.cm ~ area.cm, data = d1, ylim = c(0,75), xlim = c(0,30), col = c("red", "blue", "green")[experiment.day])
# legend(x="topright", legend = levels(d1$experiment.day), col=c("red", "blue", "green"), pch=1)
```



# Initial Shoot Morphology Analyses and Figures
##Leaf Number
```{r}
# str(d1.shoot)
# 
# #Initial Leaf Number ~ treatment x Site x Mesocosm
# bargraph.CI(x.factor = site, group = infection, response = leaf.number.D0, data = d1.shoot, ylim = c(0,6), ylab = "Leaf number", xlab = "Site", legend = TRUE)
# 
# model.leaf.no.D0 <- aov(leaf.number.D0 ~ infection * site + mesocosm, data = d1.shoot)
# anova(model.leaf.no.D0) #no effect of mesocosm so dropped
# 
# model.leaf.no.D0 <- aov(leaf.number.D0 ~ infection * site, data = d1.shoot)
# anova(model.leaf.no.D0) #Marginal effect of infection*site, significant effect of site
# 
#  #Sites tested individually
# model.leaf.no.D0.DC <- aov(leaf.number.D0 ~ infection + mesocosm, data = filter(d1.shoot, site == "DC"))
# anova(model.leaf.no.D0.DC) #no significant effects
# 
# model.leaf.no.D0.LP <- aov(leaf.number.D0 ~ infection + mesocosm, data = filter(d1.shoot, site == "LP"))
# anova(model.leaf.no.D0.LP) #no significant effects
# 
# model.leaf.no.D0.NB <- aov(leaf.number.D0 ~ infection + mesocosm, data = filter(d1.shoot, site == "NB"))
# anova(model.leaf.no.D0.NB) #no significant effects
# 
# model.leaf.no.D0.WB <- aov(leaf.number.D0 ~ infection + mesocosm, data = filter(d1.shoot, site == "WB"))
# anova(model.leaf.no.D0.WB) #marginal effect of infection, significant effect of mesocosm --> due to large variability in leaf no. between shoots
# 
# bargraph.CI(x.factor = site, group = mesocosm, response = leaf.number.D0, data = d1.shoot, ylim = c(0,6), ylab = "Leaf number", xlab = "Site", legend = TRUE)
# 
# ##WB shoots had significantly fewer leaves at the start of the experiment than shoots from DC, LP, NB. No effects of infection treatment or mesocosm on initial leaf number. Marginally significant interaction between site and infection treatment??
```

##leaf Length
```{r}
#Leaf length ~ site * treatment * leaf.no
# bargraph.CI(x.factor = leaf.no, group = infection, response = length.d0, data =  filter(d1, leaf.no != "5"), ylim = c(0,30), ylab = "Leaf length", xlab = "Site", legend = TRUE)
# 
# bargraph.CI(x.factor = leaf.no, group = site, response = length.d0, data =  filter(d1, leaf.no != "5"), ylim = c(0,30), ylab = "Leaf length", xlab = "Site", legend = TRUE)
# 
# bargraph.CI(x.factor = site, group = infection, response = length.d0, data =  filter(d1, leaf.no != "5"), ylim = c(0,30), ylab = "Leaf length", xlab = "Site", legend = TRUE)
# 
# model.leaf.length.D0 <- aov(length.d0 ~ infection * site * leaf.no + mesocosm, data = filter(d1, leaf.no != "5"))
# anova(model.leaf.length.D0) #effect of mesocosm; interaction between site and infection --> DC infected leaves are longer than non-infected DC leaves (others sites no difference); interaction between site and leaf number --> WB plants have longer 1st leaves than other sites (function of fewer leaves); LP plants have shorter 2nd leaves than other sites (b/c they are shorter plants?); NB has longer 3rd and 4rth leaves than other sites (probably due to less infection of NB plants --> less clipping)
# 
# ##Leaf 1 and 2 analyses
# bargraph.CI(x.factor = site, group = infection, response = length.d0, data =  filter(d1, leaf.no == "1"), ylim = c(0,30), ylab = "Leaf length", xlab = "Site", legend = TRUE)
# 
# bargraph.CI(x.factor = site, group = infection, response = length.d0, data =  filter(d1, leaf.no == "2"), ylim = c(0,30), ylab = "Leaf length", xlab = "Site", legend = TRUE)
# 
# model.leaf1.length.D0 <- aov(length.d0 ~ infection * site + mesocosm, data = filter(d1, leaf.no == "1"))
# anova(model.leaf1.length.D0) #only significant effect of site --> WB taller
# 
# model.leaf2.length.D0 <- aov(length.d0 ~ infection * site + mesocosm, data = filter(d1, leaf.no == "2"))
# anova(model.leaf2.length.D0) #only significant effect of site --> LP shorter
```


#Delta Length Figures
```{r}
#   #library(sciplot)
# 
# ###NOTE - only examined leaves 1 and 2 in order to capture all plants analyzed
# 
# #Leaf length
#   ## Infection (yes or no)
# bargraph.CI(x.factor = infection, response = growth, data = subset(d2, leaf.no == "1" | leaf.no == "2"), ylim = c(0,5), ylab = "Total change in leaf length (cm) over 5 days", xlab = "Infection")
# 
#   ##Infection x site
# ixs.plot <- bargraph.CI(x.factor = site, group = infection, response = growth, data = aggregate(growth ~ infection + site + mesocosm, FUN = mean, data = subset(d2, leaf.no == " 1" | leaf.no == "2")), ylim = c(0,4), ylab = "Growth (cm) over 5 days", xlab = "Site", col = c("darkgreen", "brown"))
# legend(x= "topright", legend = c("Control", "Infected"), fill = c("darkgreen", "brown"))
# 
#   ##Infection x leaf.no
# bargraph.CI(x.factor = leaf.no, group = infection, response = growth, data = d2, ylim = c(0,6), ylab = "Total change in leaf length (cm) over 5 days", xlab = "Leaf ID number", legend = TRUE)
# 
# 
#   ##Infection x mesocosm
# bargraph.CI(x.factor = infection, group = mesocosm, response = growth, data = subset(d2, leaf.no == "1" | leaf.no == "2"), ylim = c(0,5), ylab = "Total change in leaf length (cm) over 5 days", xlab = "Infection", legend = TRUE)
# 
#   ##Effect Size Infection x site
# bargraph.CI(x.factor = site, group = leaf.no, response = growth.ef, data = d2.ef, ylim = c(0,1), ylab = "Proportion growth reduction over 5 days", xlab = "Site", legend = TRUE)
```

#Delta Length Analyses
```{r}
# model.d2 <- aov(length.d5 ~ infection * site * leaf.no + length.d0 + mesocosm, data = subset(d2, leaf.no == "1" | leaf.no == "2"))
# anova(model.d2)
# 
# model.d2.B <- aov(growth ~ infection*site*leaf.no + length.d0 + mesocosm, data = subset(d2, leaf.no == "1" | leaf.no == "2"))
# anova(model.d2.B)
# library(multcompView)
# (tukey=TukeyHSD(model.d2.B))
# multcompLetters(tukey$'infection:site'[,"p adj"])
# multcompLetters(tukey$'infection:leaf.no'[,"p adj"])
# 
# ##Planned contrasts
# model.d2.B.DC <- aov(growth ~ infection*leaf.no + length.d0 + mesocosm, data = filter(d2, leaf.no == "1" | leaf.no == "2", site =="DC"))
# anova(model.d2.B.DC)
# 
# model.d2.B.LP <- aov(growth ~ infection*leaf.no + length.d0 + mesocosm, data = filter(d2, leaf.no == "1" | leaf.no == "2", site =="LP"))
# anova(model.d2.B.LP)
# 
# model.d2.B.NB <- aov(growth ~ infection*leaf.no + length.d0 + mesocosm, data = filter(d2, leaf.no == "1" | leaf.no == "2", site =="NB"))
# anova(model.d2.B.NB)
# 
# model.d2.B.WB <- aov(growth ~ infection*leaf.no + length.d0 + mesocosm, data = filter(d2, leaf.no == "1" | leaf.no == "2", site =="WB"))
# anova(model.d2.B.WB)
# 
# 
# ## Create an effect size
# ### (mean control[split by site] - individual infected)/ mean control [split by site]
# model.d2.ef.1 <- aov(growth.ef ~ site*length.d0 + mesocosm, data = subset(d2.ef, leaf.no == "1"))
# anova(model.d2.ef.1)
# 
# model.d2.ef.2 <- aov(growth.ef ~ site*length.d0 + mesocosm, data = subset(d2.ef, leaf.no == "2"))
# anova(model.d2.ef.2)
# 
# model.d2.ef <- aov(growth.ef ~ site*leaf.no*length.d0 + mesocosm, data = d2.ef)
# anova(model.d2.ef)
```

#Delta leaf.no
##Day 5 Figures
```{r}
# bargraph.CI(x.factor = infection, response = change.leaves, data = d4, ylim = c(-2,2), ylab = "Change in leaf number over 5 days", xlab = "Infection")
# 
# bargraph.CI(x.factor = site, response = change.leaves, data = d4, ylim = c(-2,2), ylab = "Change in leaf number over 5 days", xlab = "Site")
# 
# plot(no.leaves.d5 ~ no.leaves.d0, data = d4)
```

#Day 5 Analyes
```{r}
# model.d4 <- aov(no.leaves.d5 ~ infection*site + no.leaves.d0 + mesocosm, data = d4)
# anova(model.d4)
```

##Day 28 Analyses
```{r}
# model.dln28 <- aov(no.leaves.d28 ~ infection * site + no.leaves.d0 + mesocosm, data = d4)
# anova(model.dln28)
# 
# model.newleaf28 <- aov(new.leaves.d28 ~ infection * site + no.leaves.d0 + mesocosm, data = d4)
# anova(model.newleaf28)
# 
# model.leaflost28 <- aov(leaves.lost.d28 ~ infection * site + no.leaves.d0 + mesocosm, data = d4)
# anova(model.leaflost28)
# 
# (tukey=TukeyHSD(model.leaflost28))
# multcompLetters(tukey$'infection:site'[,"p adj"])
```

##Day 28 Figures
```{r}
# bargraph.CI(x.factor = site, group = infection, response = change.leaves.d28, data = d4, ylim = c(-4,4), ylab = "Change in leaf number over 28 days", xlab = "Site", legend = T)
# 
# bargraph.CI(x.factor = site, group = infection, response = new.leaves.d28, data = d4, ylim = c(0,4), ylab = "New leaves produced over 28 days", xlab = "Site", legend = T)
# 
# bargraph.CI(x.factor = site, group = infection, response = leaves.lost.d28, data = d4, ylim = c(0,4), ylab = "Leaves lost over 28 days", xlab = "Site", legend = T)
```


#Lesion Figures
```{r}
# #Lesion area
#   ##Infection x Site
# bargraph.CI(x.factor = site, group = infection, response = lesion.area.d5, data = d3.mean, ylim = c(0,10), ylab = "Lesion area (cm2) after 5 days infection", xlab = "Site", legend = TRUE)
# 
#   ##Infection x Leaf.no
# bargraph.CI(x.factor = leaf.no, group = infection, response = lesion.area.d5, data = d3, ylim = c(0,6), ylab = "Lesion area (cm2) after 5 days infection", xlab = "Leaf ID number", legend=TRUE)
# 
# #Lesion percent cover
#   ##Infection x Site
# bargraph.CI(x.factor = site, group = infection, response = percent.cover.d5, data = d3.mean, ylim = c(0,100), ylab = "Lesion percent cover after 5 days infection", xlab = "Site", col = c("darkgreen", "brown"))
# legend(x= "topright", legend = c("Control", "Infected"), fill = c("darkgreen", "brown"))
# 
#   ##Infection x Leaf.no
# bargraph.CI(x.factor = leaf.no, group = infection, response = percent.cover.d5, data = d3, ylim = c(0,100), ylab = "Lesion percent cover after 5 days infection", xlab = "Leaf ID number", legend=TRUE)
# 
#   ## Leaf.no (only leaves 1 & 2) x Site (infected leaves only)
# bargraph.CI(x.factor = site, group = leaf.no, response = percent.cover.d5, data = filter(d3, infection == 'Y', leaf.no == "1" | leaf.no =="2"), ylim = c(0,100), ylab = "Lesion percent cover after 5 days infection", xlab = "Site", legend = TRUE)
```

#Lesion Analyses
```{r}
##Area.cm2
# model.d3.A <- aov(lesion.area.d5 ~ infection * site * leaf.no + mesocosm, data = subset(d3, leaf.no == "1" | leaf.no == "2"))
# anova(model.d3.A)
# 
# (tukey=TukeyHSD(model.d3.A))
# multcompLetters(tukey$'infection:site'[,"p adj"])
# multcompLetters(tukey$'infection:leaf.no'[,"p adj"])
# 
# 
# ##Percent.cover
# model.d3.B <- aov(percent.cover.d5 ~ infection * site * leaf.no + mesocosm, data = subset(d3, leaf.no == "1" | leaf.no == "2"))
# anova(model.d3.B)
# (tukey=TukeyHSD(model.d3.B))
# multcompLetters(tukey$'infection:leaf.no'[,"p adj"])
```

#Biomass Figures
```{r}
# #Total biomass: infection x site
# bargraph.CI(x.factor = site, group = infection, response = b.t.d28, data = d1.shoot, ylab = "Total biomass (g)", xlab = "Site", ylim = c(0,1), legend = TRUE)
# 
# #above-ground: infection x site
# bargraph.CI(x.factor = site, group = infection, response = a.g.d28, data = d1.shoot, ylab = "Above-ground biomass (g)", xlab = "Site", ylim = c(0,0.7), col = c("darkgreen", "brown"))
# legend(x= "topright", legend = c("Control", "Infected"), fill = c("darkgreen", "brown"))
# 
# #below-ground: infection x site
# bargraph.CI(x.factor = site, group = infection, response = b.g.d28, data = d1.shoot, ylab = "Below-ground biomass (g)", xlab = "Site", ylim = c(0,0.4), col = c("darkgreen", "brown"))
# legend(x= "topright", legend = c("Control", "Infected"), fill = c("darkgreen", "brown"))

```

#Biomass (d.28) analyses
```{r}
# #total biomass
# model.biomass.A <- aov(b.t.d28 ~ infection * site + mesocosm, data = d1.shoot)
# anova(model.biomass.A)
# 
# #above-ground biomass
# model.biomass.B <- aov(a.g.d28 ~ infection * site + mesocosm, data = d1.shoot)
# anova(model.biomass.B)
# 
# #below-ground biomass
# model.biomass.C <- aov(b.g.d28 ~ infection * site + mesocosm, data = d1.shoot)
# anova(model.biomass.C)

```

#Rhizome length (d.28 analyses)
```{r}
# bargraph.CI(x.factor = site, group = infection, response = rhizome.length.cm.D28-rhizome.length.cm.D0, data = filter(d1.shoot, rhizome.length.cm.D0 != "NA"), ylim = c(0,8), ylab = "Rhizome growth (cm)", xlab = "Site", legend = TRUE)
# 
# model.rhizome.growth <- aov(rhizome.length.cm.D28 ~ infection * site, data = filter(d1.shoot, rhizome.length.cm.D0 != "NA"))
# anova(model.rhizome.growth) #mesocosm not significant so removed from the model
# 
# (tukey=TukeyHSD(model.rhizome.growth))
# multcompLetters(tukey$'infection:site'[,"p adj"])
# 
# ###### Planned contrasts??
# model.rhizome.growth.DC <- aov(rhizome.length.cm.D28 ~ infection, data = filter(d1.shoot, rhizome.length.cm.D0 != "NA", site == "DC"))
# anova(model.rhizome.growth.DC)
# 
# model.rhizome.growth.LP <- aov(rhizome.length.cm.D28 ~ infection, data = filter(d1.shoot, rhizome.length.cm.D0 != "NA", site == "LP"))
# anova(model.rhizome.growth.LP)
# 
# model.rhizome.growth.NB <- aov(rhizome.length.cm.D28 ~ infection, data = filter(d1.shoot, rhizome.length.cm.D0 != "NA", site == "NB"))
# anova(model.rhizome.growth.NB)
# 
# model.rhizome.growth.WB <- aov(rhizome.length.cm.D28 ~ infection, data = filter(d1.shoot, rhizome.length.cm.D0 != "NA", site == "WB"))
# anova(model.rhizome.growth.WB)
# 
# ##Effect Size
#   ##Effect Size Infection x site
# bargraph.CI(x.factor = site, response = growth.ef, data = d1.shoot.ef.rhiz, ylim = c(0,1.5), ylab = "Proportion growth reduction over 28 days", xlab = "Site", legend = TRUE)
# 
# model.rhizome.growth.ef <- aov(growth.ef ~ site, data = d1.shoot.ef.rhiz)
# anova(model.rhizome.growth.ef) #mesocosm not significant so removed from the model
# 
# (tukey=TukeyHSD(model.rhizome.growth.ef))
# multcompLetters(tukey$'site'[,"p adj"])
```


